---
title: "Alcohol vs Seat choice"
author: "Matthew Ramirez"
date: "Fall 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The Front has up to 40 people while the middle has 89 however, the back has the lowest amount of people. However the standard deviation in each seat different as the back seat has a higher amount of 12.58 than the front and middle.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

Looking at the overall data I noticed that the pr(>F) was a small value according to all the data.

```{r}
plot(TukeyHSD(model1))
```

I noticed the front-back is below the 0 point of the interval while the middle-back is the same way as the front-back as its behind the 0. However, the middle-front indicates that the the interval passes the 0 point making the family's inherently different than those behind the 0 interval. Overall the 95% family wise confidence level is the front-back and middle-back and the rest is the middle-front.

## Conclusions


